\documentclass[12pt,a4paper]{moderncv}

\usepackage[%
  paper=a4paper,
  nohead=true,
  includefoot=true,
  left=18mm,
  right=18mm,
  top=18mm,
  bottom=18mm,
  footskip=10mm
]{geometry}
\usepackage[utf8]{inputenc}

\moderncvtheme[blue]{classic}
\definecolor{see}{rgb}{0.5,0.5,0.5}
\sethintscolumnlength{0.175\textwidth}

\firstname {Alexander}
\familyname{Polovtcev}
\title     {Developer}
\phone     {+7 (921) 340-55-39}
\email     {alex.polovtcev [AT] gmail.com}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\let\ssection\section
\renewcommand{\section}[1]{\vspace*{-2ex}\ssection{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textsc{Education}}
%
\cventry{2012 -- 2014}
        {Master's Degree \textit{magna cum laude} in Software Engineering}
        {Department of Computer Systems and Software Engineering}
        {Saint-Petersburg State Polytechnical University}
        {Russia}{}

%
\cvitem{---}
       {\textsc{Master Thesis}}
\cvitem{title}
       {\emph{Instrumentation Environment for Program Analysis}}
\cvitem{description}
       {\small Software system for program characteristics analysis and
       visualization based on language-independent metamodel. Developed
       prototype supported several visualization types (CFG view, UML class
       diagrams) and simple metric calculations for programs written in Java and C.}
%
\cventry{2008 -- 2012}
        {Bachelor's Degree \textit{magna cum laude} in Software Engineering}
        {Department of Computer Systems and Software Engineering}
        {Saint-Petersburg State Polytechnical University}
        {Russia}{}
%
\cvitem{---}
       {\textsc{Undergraduate Thesis}}
\cvitem{title}
       {\emph{Development of Hardware and Software Tools for Mobile Testing System}}
\cvitem{description}
       {\small Development of some tools for an existing mobile system for
       testing uncommitted logic arrays including test loading hardware and GUI.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textsc{Experience}}
%
\cvitem{}{\textsc{Research \& Development}}
%

\cvitem{Sep 2014 -- \\ now}
{\textbf{Saint-Petersburg State Polytechnical University}\newline
 \textit{Development of enterprise information system.}\newline
         Front-end developer. My responsibilities included business-process logic and Web UI
         development using Django.}

\cvitem{Jan -- Aug 2014}
{\textbf{Saint-Petersburg State Polytechnical University}\newline
 \textit{Project on dynamic analysis tool based on program trace visualization.}
 \newline Developer of program code instrumentation system based on Clang API.}

\cvitem{Oct --  Nov 2013}
{\textbf{Saint-Petersburg State Polytechnical University}\newline
 \textit{Development of trace log analysis and visualization tool.}
 \newline Developer.}

\cvitem{Oct 2012 --\\ Aug 2013}
{\textbf{Saint-Petersburg State Polytechnical University}\newline
 \textit{Development of DSL translator for describing function semantics.}
 \newline Developer.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textsc{Personal Skills}}
%
\cvitem{}{\textbf{Operating Systems}}
\cvitem{}{Linux, Windows}
%
\cvitem{}{\textbf{Programming Languages}}
\cvitem{Proficient}{C++, Python, Java}
\cvitem{Familiar}{C, Bash, SQL}
\cvitem{Basic}{Scala, JavaScript, Lisp, Erlang}
%
\cvitem{}{\textbf{Platforms, Frameworks and Technologies}}
\cvitem{}{Java SE, Java EE, Arquillian, JUnit, Django, ANTLR, HTML+CSS}
%
\cvitem{}{\textbf{Tools}}
\cvitem{VCS}{Mercurial, Git}
\cvitem{Build Systems}{Maven, Make}
\cvitem{Databases}{PostgreSQL, Apache Derby, MongoDB}
%
\cvitem{}{\textbf{Office}}
\cvitem{}{\LaTeX, LibreOffice}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textsc{Language skills}}
%
\cvitem{Russian}{Native}
\cvitem{English}{Fluent}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textsc{Miscellaneous}}
%
\cvitem{Linkedin}
       {{\color{see}\url{ru.linkedin.com/pub/alexander-polovtcev/80/829/627/}}}
\cvitem{HeadHunter}
       {{\color{see}\url{http://spb.hh.ru/resume/cb1143fdff022f58ed0039ed1f6f4a5a43484c}}}
\cvitem{GitHub}
       {{\color{see}\url{https://github.com/Snowball239}}}
\cvitem{BitBucket}
       {{\color{see}\url{https://bitbucket.org/Snowball239}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textsc{Publications}}
%
\cvitem{}{\textsc{Conference talks}}
\cvitem{2014}
    {Aleksandr Polovtcev, Tatyana Krikun, Tatyana Vert, Aleksey Zozulya, Vladimir Itsykson.
    \textit{Visualization of parallel program execution for software behavior analysis and defect detection}
    // CEE-SECR '14 Proceedings of the 10th Central and Eastern European Software Engineering Conference in Russia
    // Article No. 24
    // ACM New York, NY, USA ©2014
    // ISBN: 978-1-4503-2889-0
}

\end{document}
